Feature importance analysis

### 2020-04-30 analysis/feature-importance.Rmd

ale_p1[[10]] = ale_p1[[10]] + scale_y_continuous(
  n.breaks = 4
)

```

@@

# Custom y axis breaks for subplots
ale_p2[[1]] = ale_p2[[1]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[2]] = ale_p2[[2]] + scale_y_continuous(
  n.breaks = 5
)
ale_p2[[3]] = ale_p2[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[4]] = ale_p2[[4]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[6]] = ale_p2[[6]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[7]] = ale_p2[[7]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[10]] = ale_p2[[10]] + scale_y_continuous(
  n.breaks = 3
)
```

@@

# Custom y axis breaks for subplots
ale_p3[[1]] = ale_p3[[1]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[2]] = ale_p3[[2]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[3]] = ale_p3[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[4]] = ale_p3[[4]] + scale_y_continuous(
  n.breaks = 4
)
```

@@

# Custom y axis breaks for subplots
ale_p4[[2]] = ale_p3[[2]] + scale_y_continuous(
  n.breaks = 4
)
ale_p4[[3]] = ale_p3[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p4[[4]] = ale_p3[[4]] + scale_y_continuous(
  n.breaks = 4
)
```

>>>>

ale_p1[[10]] = ale_p1[[10]] + scale_y_continuous(
  n.breaks = 4
)
ale_p1
```

@@

# Custom y axis breaks for subplots
ale_p2[[1]] = ale_p2[[1]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[2]] = ale_p2[[2]] + scale_y_continuous(
  n.breaks = 5
)
ale_p2[[3]] = ale_p2[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[4]] = ale_p2[[4]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[6]] = ale_p2[[6]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[7]] = ale_p2[[7]] + scale_y_continuous(
  n.breaks = 4
)
ale_p2[[10]] = ale_p2[[10]] + scale_y_continuous(
  n.breaks = 3
)
ale_p2
```

@@

# Custom y axis breaks for subplots
ale_p3[[1]] = ale_p3[[1]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[2]] = ale_p3[[2]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[3]] = ale_p3[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3[[4]] = ale_p3[[4]] + scale_y_continuous(
  n.breaks = 4
)
ale_p3
```

@@

# Custom y axis breaks for subplots
ale_p4[[2]] = ale_p3[[2]] + scale_y_continuous(
  n.breaks = 4
)
ale_p4[[3]] = ale_p3[[3]] + scale_y_continuous(
  n.breaks = 4
)
ale_p4[[4]] = ale_p3[[4]] + scale_y_continuous(
  n.breaks = 4
)
ale_p4
```
